Atlantis to SS for California Current sardines and hake: full fishing and climate scenario

### 2019-08-14 SardinesHakeatlantisom2SStest.Rmd
fixing some calcs and go single species for SS

Sadly, still a problem with the catch correction if it should match catch.txt when comverted to biomass. We are now off by about a factor of 2 (catch nums * wtAtAge is half true catch bio from the txt file):

@@

mean(sardcatchBcomp$mult)

summary(sardcatchBcomp$mult)

@@

@@

#Set species name
species <- species_ss #"Pacific_sardine" #change to species_ss to match

@@

# CV function
cv <- data.frame(species="Pacific_sardine", cv=CVs$survey)

>>>>

Sadly, still a problem with the catch correction if it should match catch.txt when converted to biomass. We are now off by about a factor of 2 (catch nums * wtAtAge is half true catch bio from the txt file), but this differs slightly by species:

@@

#mean(sardcatchBcomp$mult)

#summary(sardcatchBcomp$mult)
Filter(Negate(is.null), tapply(sardcatchBcomp$mult, sardcatchBcomp$species, summary))

@@

Now we are going single species. First we generate the inputs for sardine.

@@

#Set species name
species <- "Pacific_sardine" #change to species_ss if we want both

@@

# CV function
cv <- data.frame(species=species_ss, cv=CVs$survey)
